How Large a Sample Size is Needed for Block Bootstrap Confidence Intrvals to Have Desired Coverage Rates?

### 2023-03-01 Manuscript/manuscript.tex
comments on review section

@@

Base R has a built in function arima.sim that allows one to simulate an AR(1)
process, for which one can set the theoretical $\phi$. By default, the mean of
the process $\mu$ is 0 and the standard deviation of the error term
$\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard
deviation of the process $\sigma_{x}$ should be controlled at 1. The
observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
\begin{align}
X_{t} &= \epsilon_{t} + \phi X_{t-1};\\
Var(X_{t}) &= Var(\epsilon_{t} + \phi X_{t-1});\\
\sigma^2_{x} &= \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\\
\sigma^2_{x}(1 - \phi^2) &= 1;\\
\sigma_{x}\sqrt{1 - \phi^2} &= 1.
\end{align}
The experimental factor of this study was $\phi$, as the temporal dependence
affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a
standard normal distribution)$, 0.2, and 0.4$ were used in this study.

>>>>

\jy{set up notations for sample; give the algorithm to perform bootstrap
  procedure}

\jy{two subsections: 1) block bootstrap basics; 2) bootstrap CIs. The different
  CIs should each take a paragraph.}

\jy{Needs to distinguish the basic percentile bootstrap and corrected percentile
  bootstrap. Recall that we had trouble covering phi using the basic percentile
  method.}

@@

Base R has a built in function arima.sim that allows one to simulate an AR(1)
process, for which one can set the theoretical $\phi$. By default, the mean of
the process $\mu$ is 0 and the standard deviation of the error term
$\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard
deviation of the process $\sigma_{x}$ should be controlled at 1. The
observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new
theoretical $\sigma_{x}$ is equivalent to 1, as shown below:
\begin{align}
X_{t} &= \epsilon_{t} + \phi X_{t-1};\\
Var(X_{t}) &= Var(\epsilon_{t} + \phi X_{t-1});\\
\sigma^2_{x} &= \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x};\\
\sigma^2_{x}(1 - \phi^2) &= 1;\\
\sigma_{x}\sqrt{1 - \phi^2} &= 1.
\end{align}
The experimental factor of this study was $\phi$, as the temporal dependence
affects the performance of block bootstrap.
$\phi \in \{-0.4 -0.2, 0, 0.2, 0.4\}$.
